\begin{abstract}
Conditional Average Treatment Effect (CATE) estimation in practice
demands three properties simultaneously: heterogeneous effects
$\tau(x)$, calibrated uncertainty over them, and robustness to the
heavy tails that contaminate real outcome data. Meta-learners
\citep{kunzel2019metalearners} give (i); causal forests and BART
give (i)--(ii) with Gaussian-tail assumptions; no widely used tool
gives all three. We present \emph{Bayesian X-Learner}, an X-Learner
built on cross-fitted doubly robust pseudo-outcomes
\citep{kennedy2020optimal} with a full MCMC posterior over $\tau(x)$
via a Welsch redescending pseudo-likelihood. On Hill's IHDP benchmark
the default configuration attains mean $\PEHE = 0.56$ on 5
replications (lowest mean; differences from S-/T-/X-learners,
full-config Causal BART, and a causal forest baseline are not
significant at $\alpha = 0.05$, and rank ordering is unstable at
10 replications --- IHDP comparisons are competitive rather than
dominant). On contaminated ``whale'' DGPs
with up to 20--25\% tail density, a one-flag extension
(\texttt{contamination\_severity}) that selects a Huber-$\delta$
nuisance loss per Huber's minimax-$\delta$ relation recovers
RMSE\,$\approx$\,0.13 with tight credible intervals (single-cross-fit
30-seed coverage 83\% [Wilson 66\%, 93\%] at 20\% density;
modular-Bayes pooling with Bayesian-bootstrap nuisance draws restores
nominal 95\% coverage). We validate on the Hillstrom
email-marketing RCT ($N = 42{,}613$), demonstrating consistent
behaviour on real heavy-tailed outcome data, and report
covariate-stratified $\tau(x)$ coverage across covariate quintiles
to substantiate calibration for heterogeneous effects beyond scalar
summaries. We draw a clean
distinction between \emph{tails-as-contamination} (handled by
Welsch + Huber nuisance) and \emph{tails-as-signal} (handled by a
tail-aware CATE basis); an empirical probe confirms a tail-aware
basis recovers $\tau_{\text{tail}}$ with full subgroup coverage,
while the library's Hill-estimator path is contamination-directed and
should not be used for heterogeneous $\tau$. We map six empirical
boundaries (contamination ceiling, clean-data efficiency cost, basis
sensitivity, sample size, treatment type, compute) and show where
other tools are preferable. Code and reproducible benchmarks are released.
\end{abstract}
