\section{Background and Landscape}
\label{sec:background}

\subsection{Position in the ML/AI landscape}
Causal machine learning has moved from a statistical speciality to a
first-class ML subfield. Uplift modelling in recommender systems
\citep{wager2018estimation}, clinical decision support, and policy
optimisation all require CATE estimators that produce
\emph{heterogeneous} effects rather than a single average. What
purely predictive ML leaves on the table is calibrated uncertainty
on those effects: a point estimate of ``treatment lifts
outcome by 3 units in subgroup $A$'' is actionable only if we know
whether the confidence band crosses zero and whether the band itself
is trustworthy. Bayesian posteriors over $\tx$ supply exactly this
object --- they support downstream operations (integration,
propagation, decision rules) that point-and-bootstrap does not ---
but they are currently available only under Gaussian-tail
assumptions. Our work targets the intersection: calibrated Bayesian
$\tx$ posteriors under heavy-tailed outcome data.

\subsection{Use cases}
Four grounded applications drive the library's design:

\begin{itemize}
  \item \textbf{Clinical trials with rare severe outcomes.} Mortality
    events, adverse drug reactions, and rare efficacy spikes produce
    heavy-tailed outcome distributions. A robust posterior supports
    go/no-go decisions where bootstrap confidence intervals --- which
    inherit the resampled distribution's tail sensitivity --- are
    insufficient.
  \item \textbf{Marketing uplift with revenue whales.} Long-tailed
    customer value distributions are the norm, not the exception.
    Recovering both $\tau$ and calibrated uncertainty under whale
    contamination is what neither causal forests nor TMLE provide
    together.
  \item \textbf{Policy evaluation with structured $\tx$ hypotheses.}
    When prior knowledge suggests $\tau$ depends on specific
    features (age, dose, covariate interaction), a user-supplied
    basis $\phi(x)$ encodes the hypothesis directly and returns a
    posterior over interpretable coefficients, not an opaque
    regression surface.
  \item \textbf{Research contexts where the full posterior matters.}
    Integrating over $\tx$ to compute $P(\tx > \text{threshold})$,
    comparing posteriors across populations, or propagating
    uncertainty into downstream cost-benefit calculations. Point
    estimates plus bootstrap give the first; a Bayesian posterior
    gives all three from a single fit.
\end{itemize}

\subsection{Problems with the current landscape}

\begin{table}[!t]
\centering
\begin{tabular}{lccc}
\toprule
Tool & Heterogeneous $\tx$ & Calibrated uncertainty & Handles real tails \\
\midrule
Classical S/T/X-Learner     & \checkmark & $\times$ & $\times$ \\
EconML Causal Forest         & \checkmark & bootstrap & $\times$ \\
Causal BART                  & \checkmark & Bayesian & Gaussian only \\
TMLE / DML                    & partial    & frequentist & $\times$ \\
\textbf{Bayesian X-Learner}  & \checkmark & \checkmark (MCMC) & \checkmark (Welsch) \\
\bottomrule
\end{tabular}
\caption{Tool coverage across the three properties practitioners need.
Only the last row covers all three.}
\label{tab:landscape}
\end{table}

Classical meta-learners~\citep{kunzel2019metalearners} provide
heterogeneous $\tx$ but produce point estimates without uncertainty
quantification. Causal forests~\citep{wager2018estimation} add
bootstrap confidence intervals whose coverage on heavy-tailed outcome
distributions has not been systematically validated. Causal BART
\citep{hill2011bayesian} and BCF~\citep{hahn2020bcf} produce genuine
Bayesian posteriors via Gaussian-process-inspired tree priors, but
the likelihood is Gaussian: a single whale distorts the posterior
through its squared residual. TMLE and double machine learning
\citep[DML,][]{nie2021quasi} yield calibrated frequentist intervals
for the average effect, with CATE extensions that remain an active
research area; neither provides a Bayesian object for downstream
decision-making under tails. The last row is the position this paper
occupies: calibrated MCMC posteriors over $\tx$ with a redescending
pseudo-likelihood that tolerates real-world outcome tails.
